\documentclass[10pt]{moderncv}
\moderncvtheme{classic}
\moderncvcolor{black}

% Expand a little bit for more space
\usepackage[scale=0.85]{geometry}

\firstname{Oriana}
\lastname{Baldizan}
\title{Curriculum Vitae}
\email{oriana.baldizan89@gmail.com}

\social[linkedin][www.linkedin.com/in//orianabaldizan/]{Oriana Baldizan}
\social[github][https://github.com/oribaldi]{oribaldi}

\begin{document}
\maketitle

\section{Work Experience}


\cventry{since December 2016}{Data Engineer}
{\textsc{Allianz Technology - Global Data \& Analytics department}}{Germany}{}{%
\begin{itemize}
    \item Responsible for improving and maintaining an internal cloud platform using the Hashicorp stack.
    \item Designed and implemented software components and backend services, including ETL pipelines, REST APIs, and aggregation services.
    \item Responsible for the deployment and monitoring of services in different platforms (internal, Openshift, and Azure).
    \item Collaborated in the definition of internal best practices and participated in knowledge sharing sessions.
    \item Mentoring of junior colleagues.
    \item Technologies: Python, Flask, FastAPI, Luigi, Java, SpringBoot, Ansible, Nomad, Kubernetes, ELK, PostgreSQL, Redis, Git, Jenkins, Loki, Grafana
\end{itemize}
}

\cventry{2016}{Working Student}
{\textsc{Siemens Corporate Technology}}{Germany}{}{%
\begin{itemize}
  \item Java development for an open source Internet of Things (IoT) project.
  \item Designed and implemented REST and CoAP APIs.
  \item Main project: \href{https://github.com/thingweb/thingweb-repository}{Thingweb Repository}
  \item Technologies: Java, Javascript, HTML
\end{itemize}
}

\cventry{2013--2014}{Mobile Application Developer}
{\textsc{Mobile Media Networks}}{Venezuela}{}{%
\begin{itemize}
  \item Develop mobile applications mainly for Android.
  \item Main project: \href{https://www.thegrint.com}{The Grint}
  \item Technologies: Java, HTML5
\end{itemize}
}

\cventry{2012--2013}{Database and Computer Administrator} { BWL Laboratory - USB}{Venezuela}{}{%
\begin{itemize}
  \item Provide support and maintain computer labs (Debian and CentOS) and database systems (Oracle and PostgreSQL).
\end{itemize}
}

\section{Education}

\cventry{2014--2016}{M.Sc. Informatics with distinction}
  {Technische Universit\"at M\"unchen (TUM)}{Germany}{}{%
    Major: Machine Learning and Databases and Information Systems.
  }

\cventry{2007--2013}{B.S. Computer Science and Engineering}
  {Universidad Sim\'on Bol\'{\i}var (USB)}{Venezuela}{}{%
    Major: Machine Learning and Databases.
  }

\newcommand{\comment}[1]{}
\comment{
\section{Technical skills}

\cvitem{Programming Languages}{%
Proficient: Python, \textsc{JAVA}.
\newline
Familiar: shell scripting, Rust, Scala, C++, \LaTeX.
}

\cvitem{Data Storage}{%
  PostgreSQL, Redis, Elasticsearch. 
}

\cvitem{Software}{%
  \textsc{vi}, Git, Docker, Nomad, Kubernetes, ELK
}
}

\section{Activities and Societies}

\cventry{2015}{iOS Praktikum Summer 2015}
{\textsc{TUM}}{Germany}{}{%
\begin{itemize}
    \item Develop a mobile application in iOS (Swift) for a local industry partner.
    \item Acquired team work and project management experience.
\end{itemize}
}

\cventry{2012--2013}{Member}
{\textsc{Semantic Web Search Group}}{USB}{}{%
\begin{itemize}
    \item Group that promotes research and development among professors and students in the topic of Semantic Web.
\end{itemize}
}

\cventry{2009--2013}{Student Representative}
{\textsc{Computer Engineering Student Center and Advisory Council}}{USB}{}{%
\begin{itemize}
    \item Acquired skills and abilities for teamwork, leadership and decision making.
\end{itemize}
}

\section{Languages}

\cvitem{Native}{Spanish}
\cvitem{High}{English}
\cvitem{Elementary}{German, French}

\section{Hobbies}
\cvitem{}{Cooking, reading books, playing board games, learning about astronomy.}

\end{document}